---
title: "Glider sampling simulation figures 8 & 9"
author:
  - Doug Kinzey, AERD
date: "11/30/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
NASC.yrs = c(2001:2009,2011)
AMLR.area = c('SA','WA')
n.rep = 14
n.gldr = c(1,2,3,4,5)
save.tables = 1
max.NASC.m = 250
depths = c(150,200,300,400,500,700,1000)
azfp.off = c(150,150,150,150,150,150,150) 
qntl.vals = c(0.97,0.98,0.99,0.999,1)
smpl.st = 1
```

# Figure 8. Approximate coverage probabilities based on 9 replicates of 1, 2, 3 and 5 gliders.

```{r fig8, fig.width=7,fig.height=7, fig.show="hold", out.width="50%"}
source('Fig8.r')
Fig8(n.gldr = 1)
Fig8(n.gldr = 2)
Fig8(n.gldr = 3)
Fig8(n.gldr = 5)
```

Figure 8. Coverage probabilities for 1, 2, 3, and 5 gliders in Bransfield Strait (BS) and Cape Shirreff (CS). The expected value of 68% is shown as the dashed black line.


# Figure 9.

```{r fig9, fig.width=7,fig.height=7, fig.show="hold", out.width="50%"}
source('Fig9.r')
Fig9(AMLR.area='SA',n.rep,NASC.yrs,n.gldr)
Fig9(AMLR.area='WA',n.rep,NASC.yrs,n.gldr)
```
Figure 9. Estimated densities using the delta distribution and yos as the sampling unit ± one SD from all replicates of a single glider (lines) with a maximum yo depth of 150 m for Bransfield Strait (a) and Cape Shirreff (b), and the annual mean densities of the population (points).
