---
title: "Glider sampling simulation figure 8"
author:
  - Doug Kinzey, AERD
date: "09/22/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Figure 8. Approximate coverage probabilities based on 9 replicates of 1, 2, 3 and 5 gliders.

```{r fig8, fig.width=7,fig.height=7, fig.show="hold", out.width="50%"}
source('Fig8.r')
Fig8(gldr.pths = 1)
Fig8(gldr.pths = 2)
Fig8(gldr.pths = 3)
Fig8(gldr.pths = 5)
```

Figure 8. Coverage probabilities for 1, 2, 3, and 5 gliders in Bransfield Strait (BS) and Cape Shirreff (CS). The expected value of 68% is shown as the dashed black line.


# Figure 9.

```{r fig9, fig.width=7,fig.height=7, fig.show="hold", out.width="50%"}
source('Fig9.r')
Fig9()
Fig9(AMLR.area='WA')
```
Figure 9. Estimated densities using the delta distribution and yos as the sampling unit ± one SD from 500 replicates of a single glider (lines) with a maximum yo depth of 200 m for Bransfield Strait (a) and Cape Shirreff (b), and the annual mean densities of the population (points).
